---
title: "index"
author: "Jack Langston"
date: "8/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`ggLinearModel` is an R package created to allow users to create linear model visualizations and models. `ggLinearModel` will create a basic model with any number of polynomial predictors, a color-coded categorical variable, `parallel lines` model, models with no intercept, and more.

# Installiation
```{r}
devtools::install_github("hglanz/LinearModel-RViz-Summer2019/ggLinearModel")
```

# Usage
`ggLinearModel` is designed to create the graph and model of almost any type of linear model. Users can add a categorical variable to create models with more predictors and graphs with multiple regression lines. If someone wanted to create a quadratic model the user can increase the number of polynomial predictors which starts at 1 using the `poly` parameter. If interaction effects don't make sense to include in a model the user can drop them. Users can force the regression lines to have the same slope or the same intercept whenever they see fit. 
Users can have `ggLinearModel` return the model by making the `model` parameter set to TRUE. If a user wanted to view the coefficients they can set the `coefficient` parameter to TRUE.
A confidence interval or prediction interval at any level of confidence are both possible with `ggLinearModel`. Setting the `ci` or `pi` parameter to TRUE will produce intervals on top of the graph object. The confidence for the intervals is preset to 95%, but using the `level` parameter the user can change this.
Check out the interactive parameter to create a ggplot object that shows extra information when points and lines are being hovered over. The plotly parameter will also convert the plot object to a plotly object.

# Acknowledgments
Thank you to Dr. Hunter Glanz, and the California Polytechnic State University Statistics Department for the funding to create this package. Special thanks to the Frost Summer Scholarship Internship. 
